---
title: "Trivariate Analysis - 1 Qualitative & 2 Quantitative"
output: github_document
---

# Setup Environment

From the previous course I created the rda file for the Google Play App, also in there is the data wrangling process and original source from kaggle.com, if you want to see where the data is coming from and how it was transformed, you can take a look at [here](https://github.com/irmoralesb/BeginningDataVisualizationWithR).

Quantitative Variables

    * Ratings
    * Reviews
    * Size (Numeric)
    * Price
    
    
Qualitative Variables

    * Category
    * Installs (Install range)
    * Type (Free/Paid)
    * Content Rating
    * Genre

We are to display the relationship between:
   
    * Type, Ratings & Reviews.
    * Content Rating, Ratings & Reviews.

```{r}
library(tidyverse)
library(dslabs)
library(RColorBrewer)
library(lubridate)
load("rda/apps_versions_dataset.rda")
colors <- brewer.pal(6,"Set1")
shapes <- c(1,4,2,0,6,3)
```


# Charts/Plots

## Color-coded Scatterplot
```{r}
apps_versions_dataset %>%
  ggplot(aes(
    x = Reviews,
    y = Rating,
    color = Type)) +
  scale_color_manual(
    name = "Type",
    labels = levels(apps_versions_dataset$Type)[c(2,4)],
    values = colors) +
  geom_point() +
  ggtitle("Reviews vs Rating by Type") +
  xlab("Reviews") +
  ylab("Ratings")
```

```{r}
apps_versions_dataset %>%
  ggplot(
    aes(
      x = Reviews,
      y = Rating,
      color = Content.Rating)) +
  scale_color_manual(
    name = "Content Rating",
    labels = levels(apps_versions_dataset$Content.Rating),
    values = colors) +
  geom_point() +
  ggtitle("Reviews vs Rating by Content Rating") +
  xlab("Reviews") +
  ylab("Ratings")
```



## Shaped-coded Scatterplot
```{r}
apps_versions_dataset %>%
  ggplot(
    aes(
      x = Reviews,
      y = Rating,
      shape = Type)) +
  scale_shape_manual(
    name = "Type",
    labels = c("Free","Paid"),
    values = shapes) +
  geom_point() +
  ggtitle("Reviews vs Rating by Type") +
  xlab("Reviews") +
  ylab("Ratings")
```


```{r}
apps_versions_dataset %>%
  ggplot(
    aes(
      x = Reviews,
      y = Rating,
      shape = Content.Rating)) +
  scale_shape_manual(
    name = "Content Rating",
    labels = levels(apps_versions_dataset$Content.Rating),
    values = shapes) +
  geom_point() +
  ggtitle("Reviews vs Rating by Content Rating") +
  xlab("Reviews") +
  ylab("Ratings")
```

## Faceted Scatterplot

```{r}
apps_versions_dataset %>%
  ggplot(
    aes( 
      x = Reviews, 
      y = Rating))+
  geom_point() +
  facet_wrap( facets = ~Type) +
  ggtitle("Reviews vs Rating by Type") +
  xlab("Reviews") +
  ylab("Ratings") +
  expand_limits(y = 0)
```



```{r}
apps_versions_dataset %>%
  ggplot(aes(
    x = Reviews,
    y = Rating)) +
  geom_point() +
  facet_wrap(
    facets = ~Content.Rating) +
  ggtitle("Reviews vs Rating by Content Rating") +
  xlab("Reviews") +
  ylab("Ratings") +
  expand_limits(y = 0)
```


## Multi-series Line Chart


```{r}
typeTimeSeries <- apps_versions_dataset %>%
  filter(!is.na(Rating)) %>%
  mutate(Year = year(Last.UpdatedDate)) %>%
  select(Year,Type,Rating) %>%
  group_by(Year, Type) %>%
  summarize(Rating = mean(Rating)) %>%
  as.data.frame()

typeTimeSeries %>%
  ggplot(aes(
    x = Year,
    y = Rating,
    color = Type)) +
  geom_line() +
  ggtitle("Rating over time by Type") +
  xlab("Year") +
  ylab("Rating") +
  expand_limits(y = 0)
  
```
```{r}
contentTimeSeries <- apps_versions_dataset %>%
  filter(!is.na(Rating)) %>%
  mutate(Year = year(Last.UpdatedDate)) %>%
  select(Year, Content.Rating, Rating) %>%
  group_by(Year, Content.Rating) %>%
  summarize(Rating = mean(Rating)) %>%
  as.data.frame()

contentTimeSeries %>%
  ggplot(aes(
    x = Year,
    y = Rating,
    color = Content.Rating)) +
  geom_line() +
  ggtitle("Rating over time by Content Rating") +
  xlab("Year") +
  ylab("Rating") +
  expand_limits( y = 0)
```




## Stacked Area Chart
```{r}
typeTimeSeries %>%
  ggplot(aes(
    x = Year,
    y = Rating,
    fill = Type)) +
  geom_area()+
  ggtitle("Rating over time by Type") +
  xlab("Year") +
  ylab("Rating") +
  expand_limits(y = 0)
```

```{r}
contentTimeSeries %>%
  ggplot(aes(
    x = Year,
    y = Rating,
    fill = Content.Rating)) +
  geom_area() +
  ggtitle("Rating over time by Content Rating") +
  xlab("Year") +
  ylab("Rating") +
  expand_limits( y = 0)

```


## Faceted Line Chart
```{r}
typeTimeSeries %>%
  ggplot(aes(
    x = Year,
    y = Rating)) +
  geom_line() +
  facet_wrap(facets = ~Type) +
  ggtitle("Rating over time by Type") +
  xlab("Year") +
  ylab("Rating") +
  expand_limits(y = 0)
```

```{r}
contentTimeSeries %>%
  ggplot(aes(
    x = Year,
    y = Rating)) +
  geom_line() +
  facet_wrap( facets = ~Content.Rating ) +
  ggtitle("Rating over time by Content Rating") +
  xlab("Year") +
  ylab("Rating") +
  expand_limits( y = 0)
```

